Challenges in Developing Great Quasi-Monte Carlo Software

### 2023-02-04 MCQMC2022ChallengesQMCSoftwareArticle.tex
Updates from Overleaf

Recent interest in quality scientific software is typified by the 2021 US Department of Energy \emph{Workshop on the Science of Scientific-Software Development and Use} \cite{Her19a,ASCR-SSSDU,osti_1846008}. This workshop not only discussed diagnostics and treatments for the challenges of developing great scientific software, but also emphasized the importance of implementing theoretical advancements into well written, accessible software libraries. This section describes both the practical and theoretical importance of developing scientific software.

>>>>

Recent interest in quality scientific software is exemplified by the 2021 US Department of Energy \emph{Workshop on the Science of Scientific-Software Development and Use} \cite{Her19a,ASCR-SSSDU,osti_1846008}. This workshop not only discussed diagnostics and treatments for the challenges of developing great scientific software, but also emphasized the importance of implementing theoretical advancements into well written, accessible software libraries. This section describes both the practical and theoretical importance of developing scientific software.
